Revisiting Short-Chain Fatty Acids and the Microbiota in Colorectal Cancer

### 2018-05-21 submission/manuscript.tex
add references for scfa gene specific look

\textbf{Pulling genes involved with SCFA synthesis.} Specific genes
located near the end of the pathways involved in the synthesis of
acetate, butyrate, and propionate were analyzed for any differences
between individuals with normal colons and those with tumors. These
genes were based on pathways from KEGG and can be found in the
supplemental material {[}Table S1{]}.

\textbf{Statistical analysis workflow.} All analysis was performed using
the statistical language R (14). Generally, differences between the
different disease groups used a Kruskal-Walis rank sum test with a
Dunn's post-hoc test. Models to classify high or low SCFA concentration
based on 16S rRNA gene sequencing data were created using Random Forest
(15). Regression models to classify the exact SCFA concentration based
on 16S rRNA gene sequencing data also were built using the Random Forest
algorithm. The measured SCFA concentrations were first tested for
differences between groups. The ability of 16S rRNA gene sequencing to
classify these concentrations were then assessed. Next, the imputed gene
counts of important mediators of SCFA creation were tested. Finally, the
counts generated for OPFs that matched important genes involved with
SCFA creation were analyzed.

@@

\hypertarget{ref-r_citation_2017}{}
14. \textbf{R Core Team}. 2017. R: A language and environment for
statistical computing. R Foundation for Statistical Computing, Vienna,
Austria.

\hypertarget{ref-randomforest_citation_2002}{}
15. \textbf{Liaw A}, \textbf{Wiener M}. 2002. Classification and
regression by randomForest. R News \textbf{2}:18--22.

>>>>

\textbf{Pulling genes involved with SCFA synthesis.} Specific genes
located near the end of the pathways involved in the synthesis of
acetate, butyrate, and propionate were analyzed for any differences
between individuals with normal colons and those with tumors. These
genes were based on pathways from KEGG as well as previous research (13,
14) and can be found in the supplemental material {[}Table S1{]}.

\textbf{Statistical analysis workflow.} All analysis was performed using
the statistical language R (15). Generally, differences between the
different disease groups used a Kruskal-Walis rank sum test with a
Dunn's post-hoc test. Models to classify high or low SCFA concentration
based on 16S rRNA gene sequencing data were created using Random Forest
(16). Regression models to classify the exact SCFA concentration based
on 16S rRNA gene sequencing data also were built using the Random Forest
algorithm. The measured SCFA concentrations were first tested for
differences between groups. The ability of 16S rRNA gene sequencing to
classify these concentrations were then assessed. Next, the imputed gene
counts of important mediators of SCFA creation were tested. Finally, the
counts generated for OPFs that matched important genes involved with
SCFA creation were analyzed.

@@

\hypertarget{ref-scfa_baxter2014}{}
14. \textbf{Baxter NT}, \textbf{Zackular JP}, \textbf{Chen GY},
\textbf{Schloss PD}. 2014. Structure of the gut microbiome following
colonization with human feces determines colonic tumor burden.
Microbiome \textbf{2}:20.
doi:\href{https://doi.org/10.1186/2049-2618-2-20}{10.1186/2049-2618-2-20}.

\hypertarget{ref-r_citation_2017}{}
15. \textbf{R Core Team}. 2017. R: A language and environment for
statistical computing. R Foundation for Statistical Computing, Vienna,
Austria.

\hypertarget{ref-randomforest_citation_2002}{}
16. \textbf{Liaw A}, \textbf{Wiener M}. 2002. Classification and
regression by randomForest. R News \textbf{2}:18--22.
